The Astropy Project: \\ Sustaining and Growing a Community-oriented Open-source Project and the Latest Major Release (v5.0) of the Core Package

### 2022-03-15 src/ms.tex
comment out affil pkgs

With support from the Moore Foundation, the \astropy Project was
allocated funding to support mentoring programs. In 2020 a call was
made to submit proposals for IDE (Inclusion, Diversity, and
Empowerment) initiatives for project-wide consideration on
\github. This process was deemed the most ``open'' because it allowed
for community-wide feedback to focus and improve proposal
initiatives. Two highlighted programs that were selected and implemented via
this process are described below.

@@

\section{Conclusions}
\label{sec:conclusions}

The Astropy Project has continued to serve as an active, community-oriented
software project with a wide reach and growing impact, both within astronomy and
astrophysics and in broader scientific software communities.
The Project is in the midst of setting up infrastructure to ensure its long-term
sustainability and to continue healthy growth of the software ecosystem,
developer, and user communities that interface with the Project.
For example, over the last years, we have formalized and implemented a new
governance model for the Astropy Project (Section~\ref{sec:project-governance}),
have continued to engage a growing pool of active and top contributors
(Section~\ref{sec:project-contributors}), and have begun to receive significant
formal funding for the project itself (Section~\ref{sec:project-funding}).
The Astropy Project is also expanding its educational and community-focused
initiatives, by soliciting and funding initiatives in inclusion, diversity, and
equity (Section~\ref{sec:project-ide}) and through the Learn Astropy initiative,
which aims to make tutorials and educational content that highlight software
tools for astronomy more discoverable and accessible (Section~\ref{sec:learn}).
We expect to continue in all of these threads over the coming years as we aim to
make the Astropy Project more sustainable and a larger, more welcoming community
for open-source software users and enthusiasts in astronomy.

@@

\software{\package{astropy} \citep{astropy:2013, astropy:2018},
          \package{numpy} \citep{numpy:nature},
          \package{scipy} \citep{scipy},
          \package{matplotlib} \citep{matplotlib},
          \package{Cython} \citep{cython},
          \package{photutils} \citep{photutils},
          \package{specutils} \citep{specutils},
          \package{regions} \citep{regions},
          \package{gwcs} \citep{gwcs},
          \package{synphot} \citep{synphot},
          \package{ASDF} \citep{ASDF}.
        %   \package{SOFA} \citep{sofa},
        %   \package{ERFA} (\citealt{erfa})
          }

>>>>

With support from the Moore Foundation, the \astropy Project was
allocated funding to support mentoring programs. In 2020 a call was
made to submit proposals for IDE (Inclusion, Diversity, and
Empowerment) initiatives for project-wide consideration on
Github. This process was deemed the most ``open'' because it allowed
for community-wide feedback to focus and improve proposal
initiatives. Two highlighted programs that were selected and implemented via
this process are described below.

@@

@@

\software{\package{astropy} \citep{astropy:2013, astropy:2018},
          \package{numpy} \citep{numpy:nature},
          \package{scipy} \citep{scipy},
          \package{matplotlib} \citep{matplotlib},
          \package{Cython} \citep{cython}.
          % \package{photutils} \citep{photutils},
          % \package{specutils} \citep{specutils},
          % \package{regions} \citep{regions},
          % \package{gwcs} \citep{gwcs},
          % \package{synphot} \citep{synphot},
          % \package{ASDF} \citep{ASDF}.
          % \package{SOFA} \citep{sofa},
          % \package{ERFA} (\citealt{erfa})
          }
